### 2014-02-20 Simluations/Aspatial_fast/Figures/MPA_diffs.Rmd

>>>>

Idea, can I sub-sample the 2100 step run and take the mean of an increasingly limited window? This would mean using `df2100` as the data frame and taking the mean of all 2100 steps, and then 2099 steps, ... etc. down to 300 and seeing how the mean changes.

```{r}
int <- seq(300,2100)
names(series2100) = speeds
foo <- melt(series2100)
names(foo) <- c("biomass","speed")
means = vector("list",length(int))
names(means) = int
for(i in 1:length(int)){
  means[[i]] = ddply(foo,.(speed),function(df) avg = mean(df$biomass[1:int[i]]))
  }

bar = melt(means)
bar$variable = NULL
names(bar) = c("speed", "mean", "interval")
bar$interval = as.numeric(bar$interval)
ggplot(bar, aes(x = interval , y = mean))  + geom_line() + facet_wrap( ~ speed)
```

New idea, find the maxima and minima and take the mean of those two numbers. See if that erases the variability in means.

```{r}
int <- seq(300,2100)
names(series2100) = speeds
foo <- melt(series2100)
names(foo) <- c("biomass","speed")
means_dif = vector("list",length(int))
names(means) = int
for(i in 1:length(int)){
  means_dif[[i]] = ddply(foo,.(speed),function(df) avg=mean(max(df$biomass[1:int[i]]),min(df$biomass[1:int[i]])))
  }

bar = melt(means_dif)
bar$variable = NULL
names(bar) = c("speed", "mean", "interval")
bar$interval = as.numeric(bar$interval)
ggplot(bar, aes(x = interval , y = mean))  + geom_line() + facet_wrap( ~ speed)

ggplot(bar, aes(x = speed, y = mean, group = interval)) + geom_line(aes(colour=interval))
```

And volia! It erases that variability. Looks like I can keep the 300 time steps and take the max and minimum and take the average. So should re-do that for the existing simulation data I have and plot a contour map

```{r}
